\plaintitle

### 2016-05-27 Paper/sp2-paper.tex
Minor fixes

\begin{abstract}
One of the challenges of universities with high student populations in the Philippines is the implementation of
an online enrollment system. Many of these systems were not tested to handle sudden heavy influx of user connections
and the technologies used are not best-fitted for such occurence. In this research, we design and implement a system
that can perform well under sudden surge of users by applying recent technological advances and design techniques. 
We use Redis as the database for fast atomic database access, Rust as a language with Iron as the web server framework for faster 
serving of HTTP requests by removing the need for a garbage collector, and the split client-server architecture that allows
the offloading of heavy content to static servers. The implemented system is tested by running benchmarks on both the database and
the server that will handle HTTP requests and measuring the number of requests per second. From this, we can see how it will perform
during sudden heavy load that occur during the online registration period. The results proved the efficiency of the system by showing
that it can serve an average of 17,600 requests per second with the database serving 83,400 requests per second on a dual-core system.
Moreover, because the system is designed to be multithreaded and utilize all cores, the server should be able to linearly scale when
more cores are added making it able to serve more than 50,000 requests on a higher-end computer. In the future, improvements in the Iron
web server framework such as asynchronous IO, and faster parsing algorithms could further improve the server speed of the system
as they are some of the bottlenecks of the system.
\end{abstract}
% 
% \category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
% 
\keywords{student; information; registration; enrollment; Rust; Redis; static webapp}

@@

The backend is a server that serves a Representational State Transfer (REST)
Application Programming Interface (API) through the Hypertext Transfer Protocol
(HTTP). The system's backend shall have multithreading support. A thread will be 
spawned for every successful HTTP connection. This thread will handle its own
associated connection and wait for a command before processing it and giving a 
reply. If a command is not received or completed after a specified amount of
time, a timeout will occur and the connection will be dropped along with its
corresponding thread being deallocated from the memory.

@@

Every time a modification or addition is done on a student's schedule, the 
backend will check for conflicts before executing the specified action. 
In order to implement this, the students schedule is stored as a set of numbers
that represent the index of each 15-minute block throughout the day beginning at
7:00 AM. For example, the number represents the time from 7:00AM to 7:15AM. This
representation is also applied to the schedule of each subject.

@@

The design for the frontend tries to follow Google's Material Design 
Specification although not strictly. Along with this, it shall support mobile
platforms by implementing Responsive Design.

@@

The system's stability and efficiency were evaluated by running benchmarks on the system.
Information such as requests per second, time per request, and transfer rate
of each function are collected. The system was also be tested if it can 
handle medium and heavy workloads by using load testing tools and services.
These tests will use combinations of the different functions at ratios expected
during actual use of the system.

Benchmarks were ran on both the API server and the database management system.

The API server is benchmarked by running the tools wrk and apachebench. These two tools apply 
load to the server by running thousands of connections and recording either the number
of requests done after a certain duration or the time it takes for a specified number of requests to finish.

@@

In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400
requests per second in an Intel Core i7-5600U. It should be noted that Redis is only able to utilize a single core
so scaling through sharding will increase these numbers significantly.

>>>>

\begin{abstract}
One of the challenges of universities with high student populations in the Philippines is the implementation of
an online enrollment system. Many of these systems were not tested to handle sudden heavy influx of user connections
and the technologies used are not best-fitted for such events. In this research, we design and implement a system
that can perform well under sudden surges of users by applying the most recent technological advances and design techniques. 
We use Redis as the database for fast atomic database access, Rust as a language with Iron as the web server framework for faster 
serving of HTTP requests by removing the need for a garbage collector, and the split client-server architecture that allows
the offloading of heavy content to static servers. The implemented system was tested by running benchmarks on both the database and
the server that will handle HTTP requests and measuring the number of requests per second. From this, we can see how it will perform
during sudden heavy load that occur during the online registration period. The results proved the efficiency of the system by showing
that it can serve an average of 17,600 requests per second with the database serving 83,400 requests per second on a dual-core system.
Moreover, because the system is designed to be multithreaded and utilize all cores, the server should be able to linearly scale when
more cores are added making it able to serve more than 50,000 requests on a higher-end computer. In the future, improvements in the Iron
web server framework such as asynchronous IO, and faster parsing algorithms could further improve the server speed of the system
as they are some of the bottlenecks of the system.
\end{abstract}
% 
% \category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
% 
\keywords{student; information; registration; enrollment; Rust; Redis; static webapp}

@@

The backend is a server that serves a Representational State Transfer (REST) Application Programming Interface (API) through the Hypertext Transfer Protocol (HTTP). The implementation of the backend utilizes multithreading in order to be able to use all processor cores for the processing of HTTP requests. A thread will be spawned for every successful HTTP connection. This thread will handle its own associated connection and wait for a command before processing it and giving a reply. If a command is not received or completed after a specified amount of time, a timeout will occur and the connection will be dropped along with its corresponding thread being deallocated from the memory.

@@

Every time a modification or addition is done on the schedule of a student, the backend will check for conflicts before executing the specified action. In order to implement this, the students schedule is stored as a set of numbers that represent the index of each 15-minute block throughout the day beginning at 7:00 AM. For example, the number represents the time from 7:00AM to 7:15AM. This representation is also applied to the schedule of each subject.

@@

The design for the frontend tries to follow Material Design Specification by Google although not strictly. Along with this, it shall support mobile platforms by implementing Responsive Design.

@@

The stability and efficiency of the system were evaluated by running benchmarks on the system. Information such as requests per second, time per request, and transfer rate of each function are collected. The system was also be tested if it can handle medium and heavy workloads by using load testing tools and services. These tests will use combinations of the different functions at ratios expected during actual use of the system.

Benchmarks were ran on both the API server and the database management system. The API server is benchmarked by running the tools wrk and apachebench. These two tools apply load to the server by running thousands of connections and recording either the number of requests done after a certain duration or the time it takes for a specified number of requests to finish.

@@

In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400 requests per second on an Intel Core i7-5600U. It should be noted that Redis is only able to utilize a single core so scaling through sharding will linearly increase this serving speed.

It is also noted that the command for retrieving the schedule is processed the fastest at 140,900 requests per second. This is because it is the least complex command that consists only of a single read request to the database after input validation. On the other hand, it can be seen that the command for cancellation of subjects is processed the slowest. This is due to it being the most complex command involving input validation, retrieval and verification of enlisted subject, actuall removal of enlisted subject, retrieval of the front element in the waitlist queue, conflict checking of subject against the schedule of the waitlister, and, finally, the enlistment of the waitlister.
